---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Trials at The Neuro (Montreal Neurological Institute-Hospital)

```{r query-logs, echo = FALSE, message = FALSE}

library(dplyr)
library(ggplot2)

query_logs <- loggit::read_logs(here::here("queries.log"))

get_latest_query <- function(query, logs) {
  logs |> 
  filter(stringr::str_detect(log_msg, query)) |> 
    arrange(desc(timestamp)) |> 
    slice_head(n = 1) |> 
    pull(timestamp) |> 
    as.Date.character()
}
```

Latest AACT query: `r get_latest_query('AACT', query_logs)`

```{r trials}
trials <- readr::read_csv(here::here("data", "processed", "combined-ctgov-studies.csv"))
```

"combined-ctgov-studies.csv" contains `r nrow(trials)` ClinicalTrials.gov registrations, limited to trial registration numbers provided by McGill (excluding trials found only via AACT query).

# Prospective registration

```{r prospective-registration}
trials_pr <-
  trials |> 
  filter(
    study_type == "Interventional",
    !is.na(start_date)
  )

trials_pr |> count(is_prospective)
```

Of `r nrow(trials_pr)` interventional trials with a start date available, `r trials_pr |> filter(is_prospective) |> nrow()` are registered prospectively.

# Trial results reporting in the registry
```{r summary-results}
trials_sr <-
  trials |> 
    filter(
    study_type == "Interventional",
    recruitment_status == "Completed",
    !is.na(primary_completion_date)
  ) |> 
  mutate(
  summary_results_reporting = factor(summary_results_reporting, levels = c("results_timely", "results_due_late", "results_due_missing", "results_not_due"))
  )

trials_sr |> count(summary_results_reporting)

trials_sr |> 
  ggplot(aes(x = summary_results_reporting)) +
  geom_bar()
```

Of `r nrow(trials_sr)` interventional trials with a completed status and a primary date available, `r trials_sr |> filter(summary_results_reporting == "results_timely") |> nrow()` reported timely summary results in the registry.
